---
title: "Final Project"
subtitle: "STAT 155"
date: now
author: "Olive Pilling Chappelear, Jamie Soutter, Adam Chilbert"
date-format: "YYYY-MM-DDTHH:mm:ssZ"
format: html
editor: visual
---

# \[Title\]

Olive Pilling Chappelear, Jamie Soutter, Adam Chilbert

```{r}
#run once to use mosaic plots
#install.packages("devtools")
#devtools::install_github("haleyjeppson/ggmosaic")
```

```{r}
#load packages
library(dplyr)
library(ggplot2)
library(tidyverse)
library(ggmosaic)

#import survey data
pulse <- read.csv("pulse_of_the_nation_processed.csv")

#display data background
dim(pulse)
head(pulse)

#set indicators manually to make visualizations more readable... there has to be a better way to do this
#trump approval
pulse$trump_approval <- fct_relevel(pulse$trump_approval, "Strongly disapprove", "Somewhat disapprove", "Neither approve nor disapprove", "Somewhat Approve", "Strongly Approve")

#science is honest
pulse$science_is_honest <- fct_relevel(pulse$science_is_honest, "Strongly Disagree", "Somewhat Disagree", "Neither Agree nor Disagree", "Somewhat Agree", "Strongly Agree")

#vaccines are safe
pulse$vaccines_are_safe <- fct_relevel(pulse$vaccines_are_safe, "Strongly Disagree", "Somewhat Disagree", "Neither Agree nor Disagree", "Somewhat Agree", "Strongly Agree")

# fed sci budget
pulse$fed_sci_budget <- fct_relevel(pulse$fed_sci_budget, "Too High", "About Right", "Too Low")

#create numeric versions of factors
#fed sci budget
pulse$fed_sci_budget_numeric <- pulse$fed_sci_budget
levels(pulse$fed_sci_budget_numeric) <- c(-1, 0, 1)
pulse$fed_sci_budget_numeric <- as.numeric(as.character(pulse$fed_sci_budget_numeric))

#trump approval
pulse$trump_approval_numeric <- pulse$trump_approval
levels(pulse$trump_approval_numeric) <- c(-2, -1, 0, 1, 2)
pulse$trump_approval_numeric <- as.numeric(as.character(pulse$trump_approval_numeric))

#science is honest
pulse$science_is_honest_numeric <- pulse$science_is_honest
levels(pulse$science_is_honest_numeric) <- c(-2, -1, 0, 1, 2)
pulse$science_is_honest_numeric <- as.numeric(as.character(pulse$science_is_honest_numeric))

#vaccines are safe
pulse$vaccines_are_safe_numeric <- pulse$vaccines_are_safe
levels(pulse$vaccines_are_safe_numeric) <- c(-2, -1, 0, 1, 2)
pulse$vaccines_are_safe_numeric <- as.numeric(as.character(pulse$vaccines_are_safe_numeric))

#combine science related variables to create trust in science score
pulse$science_support <- pulse$fed_sci_budget_numeric + pulse$science_is_honest_numeric + pulse$vaccines_are_safe_numeric


```

## Introduction

Research context

Research question

-   How do gender, age, and political party affiliation affect support for science?
-   Primary research question: Can we make a model that can accurately predict whether someone will approve of Trump? (predictive)
    -   Secondary, supportive question: What are the best predictors of whether someone approves of Trump? (descriptive)

    -   Further research question: What confounding variables are there in the relationship between these seemingly silly and arbitrary variables and these serious, real world outcomes?

Research importance / consequences

## Data and Exploratory Data Analysis

```{r}
#mean, to get a sense of overall trend
pulse %>% 
  summarise(mean = mean(trump_approval_numeric))

#table of counts
pulse %>% 
  count(trump_approval)

#bar chart
pulse %>% 
  ggplot(aes(x = trump_approval_numeric)) +
  geom_bar() +
  labs(x = "Trump Approval", y = "Count")
```

Although the mean is not typically useful for categorical variables, in this scenario it does help explain the overall trend: people, on average, are slightly more likely to disapprove of Trump than approve of him. The table of counts provides further detail on this: generally, people who do not approve of trump strongly disapprove, and many fewer people feel neutral or somewhat disapprove. The distribution is bimodal, with significantly more people on the ends of the approval spectrum than in the middle, which reflects the trend of political polarization currently happening in this country.

```{r}
#Trump - Do you approve, disapprove, or neither approve nor disapprove of how Donald Trump is handling his job as president? 

#by income
pulse %>%
  ggplot(aes(x = income, y = trump_approval)) +
  geom_boxplot() +
  labs(x = "Income (thousands USD)", 
       y = "Trump approval",
        title = "Trump Approval vs Income")

#by science support
pulse %>%
  ggplot(aes(x = science_support, fill = trump_approval)) +
  geom_bar(position = "fill") +
  labs(x = "Science support", 
       y = "Relative frequency", 
       fill = "Trump approval", 
       title = "Trump Approval vs Science Support")

#by income and science support
pulse %>%
  ggplot(aes(x = income, y = trump_approval_numeric)) +
  geom_jitter(alpha = 0.25) +
  geom_smooth(se = FALSE) +
  facet_wrap(~science_support) +
  labs(x = "Income (thousands USD)",
       y = "Trump approval",
       title = "Trump Approval vs Income, Faceted Wrapped by Science Support")
```

The first two graphs seem to suggest that higher income and higher science support are associated with decreased Trump approval. But the third graph that shows income, science support, and the interaction between the two paints a very different picture. When we add regression lines and facet by science approval (which admittedly is quite messy), a pattern emerges: as science support increases, the relationship between income and trump approval weakens, and even reverses at around 3. While I'm unsure of the statistical significance of this finding given that density of the distribution also increases with science support and there are many fewer datapoints at lower science support values, this does seem to suggest that the science support factor not only affects Trump approval itself, but also interacts with the relationship between income and Trump approval.

```{r}
#factor heatmap
pulse %>%
  count(vaccines_are_safe_numeric, science_is_honest_numeric) %>%
  group_by(vaccines_are_safe_numeric) %>%
  mutate(proportion = n / sum(n)) %>%
  ggplot(aes(x = vaccines_are_safe_numeric, y = science_is_honest_numeric, fill = proportion)) +
  geom_tile() +
  scale_fill_gradient(low = "white", high = "steelblue") +
  labs(x = "Vaccines Are Safe",
       y = "Science is Honest",
       fill = "Count")
```

```{r}
trump_mod1 <- glm(trump_approval ~ income, family = "binomial", data = pulse)
summary(trump_mod1)
exp(coef(summary(trump_mod1)))

trump_mod2 <- glm(trump_approval ~ income * science_support, family = "binomial", data = pulse)
summary(trump_mod2)
exp(coef(trump_mod2))
```

```{r}
#Robots - What would you say is the likelihood that your current job will be entirely performed by robots or computers within the next decade?

#by transformer movies watched
pulse %>%
  ggplot() +
  geom_mosaic(aes(x = transformers, fill = robots))
```

Data introduction / background\
Table 1\
2-4 data visualizations

```{r}
pulse %>% 
  ggplot(aes(x = gender, fill = ghosts)) +
  geom_bar(color = "black", position = "fill") +
  scale_y_continuous(labels = scales::percent) +
  labs(x = "Gender identity", y = "", fill = "Believe in ghosts", title = "Belief in Ghosts by Gender Identity")
```

```{r}
pulse %>% 
  ggplot(aes(x = vaccines_are_safe_numeric, fill = fed_sci_budget)) +
  geom_bar(color = "black", position = "fill") + 
  scale_y_continuous(labels = scales::percent) +
  labs()
```

```{r}
pulse %>% 
  ggplot(aes(x = party, fill = fed_sci_budget)) +
  geom_bar(color = "black", position = "fill") + 
  scale_y_continuous(labels = scales::percent) +
  labs(x = "Party", y = "", fill = "Opinion on science budget", title = "Opinion on Federal Science Budget by Party Affiliation")
```

```{r}
pulse %>% 
  ggplot(aes(x = age, y = income, color = gender)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE) +
  labs(x = "Age", y = "Income", color = "Gender identity", title = "Income by Age and Gender Identity")
```

```{r}
pulse %>% 
  ggplot(aes(x = gender, y = science_support)) +
  geom_boxplot() +
  labs(title = "Support for Science by Gender Identity", x = "Gender identity", y = "Science support")
```

```{r}
pulse %>% 
  ggplot(aes(x = party, y = science_support)) +
  geom_boxplot() +
  labs(title = "Support for Science by Political Party", x = "Party", y = "Science support")
```

```{r}
pulse %>% 
  ggplot(aes(x = science_support, fill = party)) +
  geom_histogram(binwidth = 1, color = "black")


```

```{r}
pulse %>% 
  ggplot(aes(x = transformers, y = science_support)) +
  geom_smooth(method = "lm", se = FALSE)

```

```{r}
pulse %>% 
  filter(trump_approval_numeric > 0) %>% 
  count()
  labs(title = "Support for Science by Party Affiliation", x = "Party", y = "Science support")
```

## Methods

Final statistical model (method not results)\
Process for final model selection\
Hypotheses test information (method not results)

## Results

Table of coefficients\
Model message\
Coefficient discussion\
Model evaluation\
Hypothesis test results

## Conclusion

Final conclusions\
Implications\
Limitations\
Ethical considerations

## References

Include 2+ references and cite these in the paper.
