---
title: "Final Project"
subtitle: "STAT 155"
date: now
author: "Olive Pilling Chappelear, Jamie Soutter, Adam Chilbert"
date-format: "YYYY-MM-DDTHH:mm:ssZ"
format: html
editor: visual
---

# \[Title\]

Olive Pilling Chappelear, Jamie Soutter, Adam Chilbert

```{r}
#run once to use mosaic plots
#install.packages("devtools")
#devtools::install_github("haleyjeppson/ggmosaic")
```

```{r}
#load packages
library(dplyr)
library(ggplot2)
library(tidyverse)
library(ggmosaic)

#import survey data
pulse <- read.csv("pulse_of_the_nation_processed.csv")

#display data background
dim(pulse)
head(pulse)

#set indicators manually to make visualizations more readable... there has to be a better way to do this
#trump approval
pulse$trump_approval <- fct_relevel(pulse$trump_approval, "Strongly disapprove", "Somewhat disapprove", "Neither approve nor disapprove", "Somewhat Approve", "Strongly Approve")

#science is honest
pulse$science_is_honest <- fct_relevel(pulse$science_is_honest, "Strongly Disagree", "Somewhat Disagree", "Neither Agree nor Disagree", "Somewhat Agree", "Strongly Agree")

#vaccines are safe
pulse$vaccines_are_safe <- fct_relevel(pulse$vaccines_are_safe, "Strongly Disagree", "Somewhat Disagree", "Neither Agree nor Disagree", "Somewhat Agree", "Strongly Agree")

# fed sci budget
pulse$fed_sci_budget <- fct_relevel(pulse$fed_sci_budget, "Too High", "About Right", "Too Low")

#create numeric versions of factors
#fed sci budget
pulse$fed_sci_budget_numeric <- pulse$fed_sci_budget
levels(pulse$fed_sci_budget_numeric) <- c(-1, 0, 1)
pulse$fed_sci_budget_numeric <- as.numeric(as.character(pulse$fed_sci_budget_numeric))

#trump approval
pulse$trump_approval_numeric <- pulse$trump_approval
levels(pulse$trump_approval_numeric) <- c(-2, -1, 0, 1, 2)
pulse$trump_approval_numeric <- as.numeric(as.character(pulse$trump_approval_numeric))

#science is honest
pulse$science_is_honest_numeric <- pulse$science_is_honest
levels(pulse$science_is_honest_numeric) <- c(-2, -1, 0, 1, 2)
pulse$science_is_honest_numeric <- as.numeric(as.character(pulse$science_is_honest_numeric))

#vaccines are safe
pulse$vaccines_are_safe_numeric <- pulse$vaccines_are_safe
levels(pulse$vaccines_are_safe_numeric) <- c(-2, -1, 0, 1, 2)
pulse$vaccines_are_safe_numeric <- as.numeric(as.character(pulse$vaccines_are_safe_numeric))

#combine science related variables to create trust in science score
pulse$science_support <- pulse$fed_sci_budget_numeric + pulse$science_is_honest_numeric + pulse$vaccines_are_safe_numeric
```

## Introduction

Research context

Research question

-   How do gender, age, and political party affiliation affect support for science?

Research importance / consequences

## Data and Exploratory Data Analysis

```{r}
#Trump - Do you approve, disapprove, or neither approve nor disapprove of how Donald Trump is handling his job as president? 

#by income
pulse %>%
  ggplot(aes(x = income, y = trump_approval)) +
  geom_boxplot()

trump_mod1 <- glm(trump_approval ~ income, family = "binomial", data = pulse)
summary(trump_mod1)
exp(coef(summary(trump_mod1)))
```

```{r}
#Robots - What would you say is the likelihood that your current job will be entirely performed by robots or computers within the next decade?

#by transformer movies watched
pulse %>%
  ggplot() +
  geom_mosaic(aes(x = transformers, fill = robots))
```

Data introduction / background\
Table 1\
2-4 data visualizations

```{r}
pulse %>% 
  ggplot(aes(x = gender, fill = ghosts)) +
  geom_bar(color = "black", position = "fill") +
  scale_y_continuous(labels = scales::percent) +
  labs(x = "Gender identity", y = "", fill = "Believe in ghosts", title = "Belief in Ghosts by Gender Identity")
```

```{r}
pulse %>% 
  ggplot(aes(x = party, fill = fed_sci_budget)) +
  geom_bar(color = "black", position = "fill") + 
  scale_y_continuous(labels = scales::percent) +
  labs(x = "Party", y = "", fill = "Opinion on science budget", title = "Opinion on Federal Science Budget by Party Affiliation")
```

```{r}
pulse %>% 
  ggplot(aes(x = age, y = income, color = gender)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE) +
  labs(x = "Age", y = "Income", color = "Gender identity", title = "Income by Age and Gender Identity")
```

```{r}
pulse %>% 
  ggplot(aes(x = gender, y = science_support)) +
  geom_boxplot() +
  labs(title = "Support for Science by Gender Identity", x = "Gender identity", y = "Science support")
```

```{r}
pulse %>% 
  ggplot(aes(x = party, y = science_support)) +
  geom_boxplot() +
  labs(title = "Support for Science by Gender Identity", x = "Party", y = "Science support")
```

## Methods

Final statistical model (method not results)\
Process for final model selection\
Hypotheses test information (method not results)

## Results

Table of coefficients\
Model message\
Coefficient discussion\
Model evaluation\
Hypothesis test results

## Conclusion

Final conclusions\
Implications\
Limitations\
Ethical considerations

## References

Include 2+ references and cite these in the paper.
