---
title: "Final Project"
subtitle: "STAT 155"
date: now
author: "Olive Pilling Chappelear, Jamie Soutter, Adam Chilbert"
date-format: "YYYY-MM-DDTHH:mm:ssZ"
format: html
editor: visual
---

# \[Title\]

Olive Pilling Chappelear, Jamie Soutter, Adam Chilbert

```{r}
#run once to use mosaic plots
#install.packages("devtools")
#devtools::install_github("haleyjeppson/ggmosaic")
```

```{r}
#load packages
library(dplyr)
library(ggplot2)
library(tidyverse)
library(ggmosaic)

#import survey data
pulse <- read.csv("pulse_of_the_nation_processed.csv")

#set indicators manually to make visualizations more readable... there has to be a better way to do this
#trump approval
pulse$trump_approval <- fct_relevel(pulse$trump_approval, "Strongly disapprove", "Somewhat disapprove", "Neither approve nor disapprove", "Somewhat Approve", "Strongly Approve")

#science is honest
pulse$trump_approval <- fct_relevel(pulse$trump_approval, "Strongly disapprove", "Somewhat disapprove", "Neither approve nor disapprove", "Somewhat Approve", "Strongly Approve")

#vaccines are safe
pulse$trump_approval <- fct_relevel(pulse$trump_approval, "Strongly disapprove", "Somewhat disapprove", "Neither approve nor disapprove", "Somewhat Approve", "Strongly Approve")


```

## Introduction

Research context

Research question

-   What are the best predictors of whether someone approves of Trump?

-   Can we make a model that can accurately predict whether someone will approve of Trump?

-   What confounding variables are there in the relationship between these seemingly silly and arbitrary questions and these serious, real world outcomes?

Research importance / consequences

## Data and Exploratory Data Analysis

```{r}
#Trump - Do you approve, disapprove, or neither approve nor disapprove of how Donald Trump is handling his job as president? 

#by income
pulse %>%
  ggplot(aes(x = income, y = trump_approval)) +
  geom_boxplot()

trump_mod1 <- glm(trump_approval ~ income, family = "binomial", data = pulse)
summary(trump_mod1)
exp(coef(summary(trump_mod1)))
```

```{r}
#Robots - What would you say is the likelihood that your current job will be entirely performed by robots or computers within the next decade?

#by transformer movies watched
pulse %>%
  ggplot() +
  geom_mosaic(aes(x = transformers, fill = robots))
```

Data introduction / background\
Table 1\
2-4 data visualizations

## Methods

Final statistical model (method not results)\
Process for final model selection\
Hypotheses test information (method not results)

## Results

Table of coefficients\
Model message\
Coefficient discussion\
Model evaluation\
Hypothesis test results

## Conclusion

Final conclusions\
Implications\
Limitations\
Ethical considerations

## References

Include 2+ references and cite these in the paper.
