---
title: "Final Project"
subtitle: "STAT 155"
date: now
author: "Olive Pilling Chappelear, Jamie Soutter, Adam Chilbert"
date-format: "YYYY-MM-DDTHH:mm:ssZ"
format: html
editor: visual
---

# \[Title\]

Olive Pilling Chappelear, Jamie Soutter, Adam Chilbert

```{r}
#setup
library(dplyr)
library(ggplot2)
library(tidyverse)

pulse <- read.csv("pulse_of_the_nation_processed.csv")
```

## Introduction

Research context

Research question

-   What are the best predictors of whether someone approves of Trump?

-   Can we make a model that can accurately predict whether someone will approve of Trump?

-   What confounding variables are there in the relationship between these seemingly silly and arbitrary questions and these serious, real world outcomes?

Research importance / consequences

## Data and Exploratory Data Analysis

```{r}

```

Data introduction / background\
Table 1\
2-4 data visualizations

## Methods

Final statistical model (method not results)\
Process for final model selection\
Hypotheses test information (method not results)

## Results

Table of coefficients\
Model message\
Coefficient discussion\
Model evaluation\
Hypothesis test results

## Conclusion

Final conclusions\
Implications\
Limitations\
Ethical considerations

## References

Include 2+ references and cite these in the paper.
